### 2018-12-10 paper/paper.tex

\setlength{\columnsep}{1cm}
%\addbibresource{paper.bib}
%\nocite{*}
\sectionfont{\fontsize{12}{15}\selectfont}
\subsectionfont{\fontsize{12}{15}\selectfont}

\begin{document}
    \begin{center}
        \textbf{Evaluation of Classifiers and Feature Selection on Spam Filtering test} 
    \end{center}

@@

            The next step is to extract the necessary features and then vectorize
            them for training with our classifier. The first step of extraction was
            to

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}
                \label{spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}
                \label{ham_wc}
             \end{minipage}
            This is more text

@@

@@

        %\section{References}
        % \printbibliography
    \end{multicols}
\end{document}

>>>>

\setlength{\columnsep}{1cm}

\sectionfont{\fontsize{12}{15}\selectfont}
\subsectionfont{\fontsize{12}{15}\selectfont}

\begin{document}
    \begin{center}
        \textbf{Evaluation of Classifiers and Feature Selection on Spam Filtering} 
    \end{center}

@@

            The next step is to extract the necessary features and then vectorize
            them for training with our classifier.

            \begin{Figure}
                \centering
                \includegraphics[scale=0.5]{figures/extract.png}
                \captionof{figure}{Extraction Process}
                \label{fig:extrac}
            \end{Figure}

            The first step of extraction was
            to find words that meant the most to the corpus which we defined as
            the body of the email. To accomplish this
            we used the tf-idf algorithm implemented in scikit-learn. This algorithm helps
            weigh down words that are too common, and bring up words that are important
            to the corpus. Next we split the documents into spam and ham before analysis.
            This was done because this algorithm is still based on frequency and the
            ratio of ham to spam was not 1:1. Characteristic words to spam emails such
            as ``free'' wouldn't show up because they're not prominent in ham emails.

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}\label{fig:spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}\label{fig:ham_wc}
             \end{minipage}

             Figures \ref{fig:spam_wc} and \ref{fig:ham_wc} show
             the most prominent 50 words in the corpus. Most the the words in the
             ham word cloud relate to business operations asking someone to do about
             task or getting times and dates of events. When you look at the spam
             word cloud you see a few similar words such as ``mail'' or ``get''.
             But in general you see words that you would associate with someone trying
             to get you to send them money or buy a product. Words like ``money'',
             ``offer'' and ``order'' are the epitome of this.

             We followed this same process for extracting features for the title, but
             we kept the features separate as a title's content may have more distinct
             patterns compared to the body of an email

@@

        %\section{Classifier Selection}

@@

        %\section{References}
        % \printbibliography
        \section{Conclusion}

            This paper has shown that the usage of machine learning alone can preform
            the classification well, compared to other's results our metrics are lower
            than the other paper's we are comparing ourselves against. Adding more features
            that aren't word based may help even more with performance and also increasing the
            size of the dataset would help as well. We also recognize the limitations of
            this implementation lends itself to only classify emails from the early 2000s, as
            we did no testing on modern email data which may have a distribution that doesn't
            work well with our implementation.
        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}
